Improving the Replicability of Psychological Science Through Pedagogy

### 2017-08-09 paper/paper.Rmd
add funding
resubmitted ampps

We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study (see @simmons2011).

@@

Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class. 
We are grateful to the authors of the original studies who provided materials and gave extensive comments on an earlier draft of this manuscript.

@@

@@

All reported results are from pre-registered, confirmatory analyses. In two cases, in final review of the projects (after data analysis), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim. In both of these cases, the original authors had fit regression models to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis. After discussion, the instructor team converged on a statistical test that they thought better corresponded to the original authors' intended hypothesis of interest. We report results from these corrected tests here. We return to this issue below, as we believe that test selection is a critical theoretical issue in replication research (see e.g., @monin2016 for discussion).

@@

This vision of collaborative pedagogical replication requires instructors to make class results more broadly discoverable. We can envision a number of possible avenues for this kind of sharing. For example, if some products are shared openly in a repository like the Open Science Framework (osf.io) or figshare (figshare.com) and tagged appropriately, they will be discoverable via search engines. Alternatively, a more structured method for sharing and discovery would be upload to specific replication curation websites like PsychFileDrawer (psychfiledrawer.org) or CurateScience (curatescience.org). Both of these models assume limited coordination across instructors, but more structured collaborations are of course possible. For example, the Collaborative Replications and Education Project (osf.io/wfc6u) selected a subsample of important and feasible studies for replication and helped provide materials to instructors with the explicit goal of encouraging cross-lab pedagogical replications. On these models, instructors must of course curate which projects are released publicly. But by pre-specifying review criteria, instructors can incorporate dissemination into their course as a reward for high quality work.

>>>>

We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study [see @simmons2011].

@@

Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class. This material is also based upon work supported by the National Science Foundation Graduate Research Fellowship under Grant No. DGE-1656518.
We are grateful to the authors of the original studies who provided materials and gave extensive comments on an earlier draft of this manuscript.

@@

All reported results are from pre-registered, confirmatory analyses. In two cases, in final review of the projects (after data analysis), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim. In both of these cases, the original authors had fit regression models to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis. After discussion, the instructor team converged on a statistical test that they thought better corresponded to the original authors' intended hypothesis of interest. We report results from these corrected tests here. We return to this issue below, as we believe that test selection is a critical theoretical issue in replication research [see e.g., @monin2016 for discussion].

@@

@@

This vision of collaborative pedagogical replication requires instructors to make class results more broadly discoverable. We can envision a number of possible avenues for this kind of sharing. For example, if some products are shared openly in a repository like the Open Science Framework (http://osf.io) or figshare (http://figshare.com) and tagged appropriately, they will be discoverable via search engines. Alternatively, a more structured method for sharing and discovery would be upload to specific replication curation websites like PsychFileDrawer (http://psychfiledrawer.org) or CurateScience (http://curatescience.org). Both of these models assume limited coordination across instructors, but more structured collaborations are of course possible. For example, the Collaborative Replications and Education Project (http://osf.io/wfc6u) selected a subsample of important and feasible studies for replication and helped provide materials to instructors with the explicit goal of encouraging cross-lab pedagogical replications. On these models, instructors must of course curate which projects are released publicly. But by pre-specifying review criteria, instructors can incorporate dissemination into their course as a reward for high quality work.
